The Astropy Project

### 2017-12-11 registry.tex
correct several serious issues with table formatting

\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J. Xavier Prochaska, Nicolas Tejos, and Neil Crighton &  \\
\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs} \\

@@

\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, Erik Tollerud &  \\
\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm &  \\

>>>>

\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & \parbox{3in}{J. Xavier Prochaska,  Nicolas Tejos,  and Neil Crighton} &  \\
\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther & \citealt{marxs} \\

@@

\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & \parbox{3in}{Nicholas Earl,  Adam Ginsburg,  Steve Crawford,\par  Erik Tollerud} &  \\
\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & \parbox{3in}{Daniela Huppenkothen,  Matteo Bachetti,  Abigail Stevens,\par  Simone Migliari,  and Paul Balm} &  \\
